% Packages
\documentclass[a4paper,11pt]{article}
\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage{fontawesome}
\usepackage[colorlinks=true, linkcolor=black, urlcolor=black, citecolor=black, pdfnewwindow=true]{hyperref}
\usepackage{fancyhdr}
\usepackage{ragged2e}
\setlength{\footskip}{1cm}
\pagestyle{fancy}
\fancyhf{}
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}
% Adjust margins
\addtolength{\oddsidemargin}{-0.530in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.45in}
\addtolength{\textheight}{1in}
\urlstyle{rm}
% Contact Links
\newcommand{\linkedinLink}{https://ro.linkedin.com/in/catalin-butacu}
\newcommand{\githubLink}{https://github.com/CatalinButacu/}
\newcommand{\emailLink}{mailto:butacu.catalin@yahoo.com}
\newcommand{\phoneLink}{tel:+40753320964}
% Certificate Links
\newcommand{\oracleAnalyticsCloudLink}{https://catalog-education.oracle.com/ords/certview/sharebadge?id=2D550AA768AD738FC822D0745D8F71CC4845A22B212DA7CE9CF27259DE5EEAAF}
\newcommand{\oracleDataScienceLink}{https://catalog-education.oracle.com/ords/certview/sharebadge?id=277E72156AC389D08A7C467084A3CE568D1D9078A9A8301005E9BCC3E31FA903}
\newcommand{\oracleVectorSearchLink}{https://catalog-education.oracle.com/ords/certview/sharebadge?id=08BDD5D7DA29BEFF7F764053FD58DD5D7536402E95B847A926A53027CC0C1FCC}
\newcommand{\oracleGenAILink}{https://catalog-education.oracle.com/pls/certview/sharebadge?id=36F42AE9CD423CBEDFC5C81160E753619C6EC388D2CA3FB3FDBB2700CD1BE2AB}
\newcommand{\oracleAIFoundationsLink}{https://catalog-education.oracle.com/pls/certview/sharebadge?id=615C9F04543C7A32303E280E44615A75F07207864CD9E6FA301C63CE57A7FDD9}
\raggedbottom
\justifying
\setlength{\tabcolsep}{0in}
% Sections formatting
\titleformat{\section}{
  \vspace{-10pt}\scshape\raggedright\large\color{NavyBlue}
}{}{0em}{}[\color{NavyBlue}\titlerule \vspace{-6pt}]
%-----------------------------------------------------------------
% Custom commands
\newcommand{\resumeItem}[1]{\item\small{#1\vspace{-2pt}}}
\newcommand{\resumeItemWithoutTitle}[1]{
  \item\small{
    {\vspace{-2pt}}
  }
}
\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \color{NavyBlue}\textbf{#1} & #2 \\
      #3 & #4 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubheadingSimple}[2]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & #2 \\
    \end{tabular*}\vspace{-5pt}
}
\newcommand{\resumeSubItem}[2]{\resumeItem{\textbf{#1}}{#2}\vspace{-3pt}}
\renewcommand{\labelitemii}{$\circ$}
\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}
%---------------------------------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%
\begin{document}
%----------HEADING----------------------------------
\noindent\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
   \color{NavyBlue}\textbf{{\LARGE BUTACU IONEL-CATALIN}} & \\  
   \small{\hspace*{-2pt}
     \href[pdfnewwindow=true]{\linkedinLink}{linkedin.com/in/catalin-butacu\ \faExternalLink}  \textbullet 
     \href[pdfnewwindow=true]{\githubLink}{github.com/CatalinButacu\ \faExternalLink}        \textbullet 
     \href[pdfnewwindow=true]{\emailLink}{butacu.catalin@yahoo.com\ \faExternalLink}        \textbullet 
     \href[pdfnewwindow=true]{\phoneLink}{0753 320 964}
   }
 \end{tabular*}
%----------------------------------PROFESSIONAL SUMMARY----------------------------------
\section{Professional Summary}
\begin{justify}
\small{Software Engineer with a background in computer engineering, specializing in C++ and Qt framework for desktop application development. Expertise in concurrent programming, API development, and system architecture, with a focus on integrating AI solutions. Certified in leading cloud technologies and continuously advancing machine learning expertise through practical projects and advanced coursework.}
\end{justify}
%----------------------------------EXPERIENCE----------------------------------
\vspace{-5pt}
\section{Professional Experience}
\resumeSubHeadingListStart
  \resumeSubheading{Gemini CAD Systems}{Iași, RO}{Junior Software Engineer}{June 2023 - Present}
  \resumeItemListStart
      \resumeItem{Developed complex desktop applications using C++ and Qt framework, encompassing UI components, business logic, and data management layers, with a focus on delivering comprehensive features and functionality.}
      \resumeItem{Designed and implemented action classes and controller implementations for 2D canvas operations, incorporating concurrent behavior and refresh mechanisms for pattern design updates.}
      \resumeItem{Architected model serialization/deserialization systems with versioning support, ensuring backward compatibility for legacy pattern files while collaborating with cross-functional teams on data structure architecture.}
      \resumeItem{Engineered cloud communication infrastructure for 3D team integration, implementing event-driven data transmission protocols and synchronization mechanisms.}
      \resumeItem{Participated in the migration of the Qt framework from version 5.8 to 6.12, updating deprecated APIs and ensuring component compatibility while coordinating with the development team to resolve migration challenges.}
      \resumeItem{Implemented comprehensive internationalization systems, including tooltips, multi-language translations, and role-based user permission frameworks for garment measurement tools and avatar dimension features.}
  \resumeItemListEnd
  \resumeSubheadingSimple{Software Engineer Intern}{August 2022 - May 2023}
  \resumeItemListStart
      \resumeItem{Utilized Qt meta-object signal/slot paradigms to develop real-time UI interactions and event-driven communication architectures.}
      \resumeItem{Developed static UI components and executed refactoring initiatives to enhance visual consistency and rendering performance across cross-platform environments.}
      \resumeItem{Employed Git/GitLab workflows, Jenkins CI/CD automation pipelines, and Scrum agile methodologies to streamline software delivery cycles.}
  \resumeItemListEnd
  \resumeSubheading{Special Telecommunications Service (STS)}{Botosani, RO}{IT Support Staff (Local Election)}{August 2020 - September 2020}
  \resumeItemListStart
      \resumeItem{Provided technical support for electoral IT infrastructure (SIMPV/SICPV systems) and implemented robust cybersecurity protocols during national election processes.}
      \resumeItem{Conducted comprehensive training programs and provided technical assistance for electoral personnel, ensuring system availability and equipment functionality through proactive monitoring and incident response.}
  \resumeItemListEnd
\resumeSubHeadingListEnd
%----------------------------------EDUCATION----------------------------------
\vspace{-5pt}
\section{~~Education}
\resumeSubHeadingListStart
  \resumeSubheading{Gheorghe Asachi Technical University of Iași}{Iași, RO}{Master of Science in Artificial Intelligence}{October 2024 - June 2026}
    {\par\footnotesize \textit{\textbf{Advanced Coursework:} Deep Neural Networks, Machine Learning Fundamentals, Natural Language Processing (NLP), Reinforcement Learning, Multi-Agent Systems, Cloud Computing Architecture, Big Data Techniques, Edge Computing Applications}}
  \vspace{-5pt}
  \resumeSubheadingSimple{Bachelor of Science in Automatic Control and Applied Informatics}{October 2020 - June 2024}
    {\par\footnotesize  \textit{\textbf{Core Curriculum:} Advanced Computer Programming, Data Structures \& Algorithms, Database Management Systems, Real-Time Programming, Systems Theory, Microprocessor-Based Systems, Embedded Systems Engineering, Control Engineering, Computer Networks, Neural Networks \& Fuzzy Logic, Knowledge-Based Systems}}
\resumeSubHeadingListEnd
%----------------------------------Awards----------------------------------
\section{Professional Certifications}
\begin{description}[font=$\bullet$]
  \item {\href[pdfnewwindow=true]{\oracleAnalyticsCloudLink}{Oracle Analytics Cloud 2025 Certified Professional (1Z0-1041-25)\ \faExternalLink}}                \vspace{-5pt}
  \item {\href[pdfnewwindow=true]{\oracleDataScienceLink}{Oracle Cloud Infrastructure 2025 Data Science Professional (1Z0-1110-25)\ \faExternalLink}}        \vspace{-5pt}
  \item {\href[pdfnewwindow=true]{\oracleVectorSearchLink}{Oracle Cloud Infrastructure 2025 AI Vector Search Professional (1Z0-184-25)\ \faExternalLink}}     \vspace{-5pt}
  \item {\href[pdfnewwindow=true]{\oracleGenAILink}{Oracle Cloud Infrastructure 2025 Generative AI Professional (1Z0-1127-25)\ \faExternalLink}}       \vspace{-5pt}
  \item {\href[pdfnewwindow=true]{\oracleAIFoundationsLink}{Oracle Cloud Infrastructure 2025 AI Foundations Associate (1Z0-1122-25)\ \faExternalLink}}         \vspace{-5pt}
\end{description}
%----------------------------------PROJECTS----------------------------------
\section{Technical Projects \& Research}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small\item
    \textbf{AI-Enhanced Firewall \& Intrusion Detection System} \hfill\textbf{2025} \\
     \footnotesize{Architected an AI-enhanced firewall with dynamic attack signature learning and real-time recognition of novel attack patterns. Validated against active penetration attempts.}
    \small\item
    \textbf{Ant Colony Optimization (ACO) Agent Simulation} \hfill\textbf{2025} \\
     \footnotesize{Designed and implemented a multi-agent simulation of Ant Colony Optimization for complex pathfinding problems on connected graphs. Conducted comparative analysis of return strategies.}
    \small\item
    \textbf{Real-Time Hand Sign Recognition on Edge NPU} \hfill\textbf{2025} \\
     \footnotesize{Developed a high-performance gesture recognition system using a custom ONNX model trained on the HaGRID dataset. Optimized inference for NXP Neurological Processing Units (NPU).}
    \small\item
    \textbf{RAG-Powered Pharmaceutical Assistant (Hackathon)} \hfill\textbf{2025} \\
     \footnotesize{Co-engineered a RAG-based pharmaceutical chatbot during a hackathon. Implemented the query engine for precise medication data and contraindications.}
    \small\item
    \textbf{Advaed Metaheuristic Optimization Framework} \hfill\textbf{2025} \\
     \footnotesize{Co-developed a Python-based optimization framework featuring multiple metaheuristic algorithms. Implemented specialized solvers for high-dimensional optimization problems.}
    
    \small\item
    \textbf{WiDS Datathon 2025 University Edition - Top 10 Finalist} \hfill\textbf{2025} \\
     \footnotesize{Achieved 8th place in the Women in Data Science University Edition by developing regression models for neuroimaging analysis. Engineered ML pipelines for age prediction using fMRI data.}
    
\end{itemize}
%----------------------------------Volunteer Experience----------------------------------
\section{Leadership \& Volunteer Experience}
\resumeSubHeadingListStart
    \resumeSubheading{LOCAL BEST GROUP IASI}{Iași, RO}
    {IT Department Coordinator \& Technical Lead}{September 2023 - August 2024}
    \resumeItemListStart
        \resumeItem{Coordinated IT department operations and managed technical infrastructure to support organizational activities.}
        \resumeItem{Supervised a team of IT volunteers, providing technical guidance and coordinating project execution.}
        \resumeItem{Managed IT resources, including hardware assets, software licensing, and network infrastructure.}
    \resumeItemListEnd
    \vspace{-1pt}
    \resumeSubheadingSimple{Event Coordinator - JobShop® Career Event (23rd Edition)}{November 2022 - April 2023}
    \resumeItemListStart
        \resumeItem{Planned and executed the JobShop® Career Event, facilitating connections between students and industry employers.}
        \resumeItem{Coordinated event logistics, including venue management, vendor coordination, scheduling, and budget oversight.}
        \resumeItem{Developed event strategies to enhance attendee engagement and partner satisfaction.}
        \resumeItem{Facilitated communications with executives, university administration, and volunteer teams.}
    \resumeItemListEnd
    \vspace{-1pt}
    \resumeSubheadingSimple{TOPICS Responsible | Prove It 24H Techathon (2nd Edition)}{December 2021 - March 2022}
    \resumeItemListStart
        \resumeItem{Collaborated with university departments and stakeholders to define event scope and technical requirements for the hackathon.}
        \resumeItem{Managed participant experience from establishing technical regulations to providing hackathon resources and infrastructure.}
        \resumeItem{Coordinated communication between organizers, industry mentors, and participants during the 24-hour competition.}
    \resumeItemListEnd
    \vspace{-1pt}
    \resumeSubheadingSimple{IT Responsible | BEST Training Weekend}{January 2021 - May 2022}
    \resumeItemListStart
        \resumeItem{Developed a responsive event website using HTML5, CSS3, and JavaScript.}
        \resumeItem{Collaborated with design and marketing teams to resolve UI and JavaScript issues during event operations.}
    \resumeItemListEnd
\resumeSubHeadingListEnd
%----------------------------------CORE COMPETENCIES----------------------------------
\vspace{-5pt}
\section{TECHNICAL SPECIALTIES}
\begin{itemize}[leftmargin=0.15in, label={}, noitemsep, topsep=0pt, parsep=0pt, partopsep=3pt]
    \small\item \textbf{Programming Languages:} C++17/20, Python, Java, JavaScript (ES6+), SQL, Bash/PowerShell
    \small\item \textbf{Frameworks \& Libraries:} Qt Framework (5.8-6.12), PyTorch, TensorFlow, Scikit-Learn, Keras
    \small\item \textbf{Software Development:} Object-Oriented Programming, Design Patterns, Software Architecture, Concurrent Programming, Real-Time Systems
    \small\item \textbf{Development Practices:} Agile/Scrum, Code Reviews, Git/GitLab, CI/CD Pipelines, Unit Testing
    \small\item \textbf{Performance Optimization:} Multithreading, Memory Management, Code Refactoring, Profiling, Debugging
    \small\item \textbf{AI/ML Technologies:} Machine Learning, Deep Learning, Natural Language Processing (NLP)
    \small\item \textbf{Cloud \& DevOps:} Oracle Cloud (OCI), AWS, Azure, Docker, Jenkins, CI, Technical Documentation
    \small\item \textbf{Tools \& Platforms:} Jupyter/Colab, Anaconda, Weights \& Biases, Qt Widgets, QML, Signal/Slot, MVC
\end{itemize}
\vspace{-5pt}
\section{ADDITIONAL SKILLS}
\begin{itemize}[leftmargin=0.15in, label={}]
    \small\item \textbf{Soft Skills:} Technical Mentoring, Cross-Functional Collaboration, Agile Project Management, Problem Solving
\end{itemize}
\end{document}
